---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# TCMR

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of TCMR is to ...

## Installation

You can install the released version of TCMR from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("TCMR")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("saisaitian/TCM_Microarray")
```
## Example

This is a basic example which shows you how to solve a common problem.

### Load example dataset

```{r}
library(TCMR)
data <- load_example_dataset()
```

### Load analyzed DEG data

```{r}
data("AnalyzedDEG")
head(AnalyzedDEG)
```

Use a subset of `AnalyzedDEG` to select corresponding DEG results.

```{r}
head5_reports <- head(AnalyzedDEG) %>% 
  load_analyzedDEG()

str(head5_reports, max.level = 1)
```

```{r}
one_report <- load_analyzedDEG(2)
head(one_report)
```

### Run DEG analysis

```{r}
ix <- c(1, 2, 61, 62)
expr <- data$expr[, ix]
group <- data$pdata$perturbagen[ix]

# Run DEG analysis
report <- deg_caller(expr, group = group, level = group[c(3, 1)])
head(report)
```


See `?deg_caller` for more details.
